### 2011-06-18 thesis/introduction.tex
Introduction chapter finished

\section{Motivation}
% Detect limitations and novel knowledge

Deploy to new environments, long-term and active learning,
understand of limitations of the existent knowledge
reliability

Example of what kind of an high-level thinking on space and its semantics can
provide: Get me a beer/milk concept.

% == Reasoning about need for Novelty Detection ==
%
% Dynamic environment (inability to know the environment or even to be possible
% to map all semantic concepts to interact with humans).
%
% Knowledge-Awareness (knowing what we know... And detecting novel cases)
% Identify gaps in the semantic knowledge.
% Automatic detection and learning of novel concepts.
%
% Increase robustness
% Self-Extending
%

\section{Problem}
% Deal with uncertainty -> need for probabilistic models.
% Deal with semantic    -> need of structured models such as graphical models.

They need to possess ability to adapt to situations as its infeasible to rely
on extensive man-work to tag objects, map space and code all the aspects that
make up our human-reality.

Lack of methods that are able to detect gaps on their
Study how structure changes novelty

Being able to represent all this type of knowledge is an huge task on itself and this thesis
focus mainly on how to detect novelty on semantic values  
Pronobis~\cite{pronobis2011phd} has tackled this problem by proposing

\section{Proposal}

% Extend a probabilistic graphical modelling framework with capabilities to
% detect novelty.
% Both in terms of novel classes as of novel structure.
%
Given a probabilistic structure representing the sensed conceptual knowledge
obtained by the agent develop methods able to detect novelty present
either on new semantic concepts (new classes) or even on structure that was
previously unknown.

For that the probabilistic semantic representation presented by
\cite{pronobis2011phd} is used.

% If everything goes fine... 2 of the "Future Directions" proposed are 
% Novelty Detection and Learning of Novel Concepts:
%  Identify Gaps in Spatial and Semantic Knowledge -> Addressed
%  Performing learning of new concepts -> Outside Scope / No Time
%
% Using Properties for Space Segmentation
%  If we move on detecting novel structures on the graph we are addressing this
%  issue.

>>>>

\section{Motivation}
% Detect limitations and novel knowledge
It is highly desirable that a robot can be deployed to new and unknown environments. Aiming at that,
a robot has to perform its own semantic mapping of the environment instead of relying on a provision
of already labelled maps.
But the semantic mapping ability of a robot is restricted by its spatial and semantic knowledge.
This poses a problem as its unrealistic to believe that on unknown environments the robot knowledge
is complete. So it becomes important to detect gaps on the robot knowledge, such that the robot can
be aware of limitations of its models and devise techniques to not fail victim of its limitations.

Additionally the detection of knowledge gaps, will serve as base for several other problems in
artificial intelligence such as active-learning and maintenance of long and life-long knowledge.

\section{Proposal and Goals}
This thesis aims at developing methods that can be used to detect gaps on the semantic knowledge
of an agent. For that the spatial knowledge representation proposed in \cite{pronobis2010ias} will
be used as base defining the agent knowledge.
Given an instance world, that knowledge, is used to perform semantic mapping~\cite{pronobis2011semmap}
on indoor environments using a probabilistic graphical model. That model is instantiated from the
environment using the spatial knowledge and captures both semantic and structural information of
space. It allows the agent to map all the modelled variables in the presence of uncertainty and 
therefore this thesis will focus on study and developing methods that can detect novel semantic room
categories from it.

% Study how structure changes novelty.
% If everything goes fine... 2 of the "Future Directions" proposed are 
% Novelty Detection and Learning of Novel Concepts:
%  Identify Gaps in Spatial and Semantic Knowledge -> Addressed
%  Performing learning of new concepts -> Outside Scope / No Time
%
% Using Properties for Space Segmentation
%  If we move on detecting novel structures on the graph we are addressing this
%  issue.
